Characterize the fetal kidney reference from the kidney cell atlas

### 2024-08-19 analyses/cell-type-wilms-tumor-06/notebook_template/00b_characterize_fetal_kidney_reference_Stewart.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/00b_characterize_fetal_kidney_reference_Stewart.Rmd
Co-authored-by: Jaclyn Taroni <19534205+jaclyn-taroni@users.noreply.github.com>

---
title: "Characterize the fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  url: https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---

>>>>

---
title: "Characterize the fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---
